---
title: "Your Awesome Title"
author: "Author One^1^* and Author Two^2^"
date: '`r format(Sys.time())`'
format: 
  pdf:
    toc: false
    colorlinks: true
    include-before-body: template/doc_prefix.tex
    include-in-header: template/preamble.tex
    keep-tex: true
  html: default
  docx:
    reference-doc: template/nature_style.docx
editor: source
crossref: 
  fig-prefix: Fig.
fontsize: 12pt
linestretch: 1.5
link-citations: yes
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/ecology.csl
bibliography: ref.bib
always_allow_html: yes
links-as-notes: true
notes-after-punctuation: false
---


\footnotesize 

^1^Department of Biological Sciences, Louisiana State University, Baton Rouge, LA, USA  
^2^Center for Computation & Technology, Louisiana State University, Baton Rouge, LA, USA

\* **Corresponding author**, email: daijianglee@gmail.com; 125 Life Science Building, Baton Rouge, LA 70803

\normalsize

**Running headline**: Environment and species richness

**Abstract**: Your awesome abstract here.

\clearpage

# Introduction

Here is your introduction. It should describe clearly the rationale for the study being done and the previous work related with the study. It should also tell readers about your specific hypothese/questions being addressed. Citations will be like this [@adair_single-pool_2010], or [e.g., @clark_loss_2008], or [@eriksson_seed_1993; @williamson_dissolved_1999]

Here is the second paragraph of the introduction. 


# Methods

Here is the method section. You can include equations easily. For inline equations, use $\text{var}(X) = p(1-p)$. For display equation, use

$$\text{var}(X) = p(1-p)$$

## Results


#### Tables

Insert tables by `kable` in knitr package in R. Then cross-reference it back with: see @tbl-tableName. In order for a table to be cross-referenceable, its label must start with the `tbl-` prefix.


```{r}
#| label: tbl-tableName
#| tbl-cap: "**Model coefficients of leaf senescence based on in situ data**." 
#| echo: false
#| results: 'asis'
#| message: false
#| warning: false
source(here::here("R/rcode.R"))
# linesep = c('', '', '', '', '', '\\addlinespace') 
# can be used within kable to specify linespace
knitr::kable(iris[1:5, 1:3], booktabs = T) |> 
 kableExtra::kable_styling(bootstrap_options = c("striped", "scale_down", "condensed", "hover"), 
                           latex_options = c("striped", "HOLD_position")) # , "scale_down"
```

Put results inline, e.g. the mean species richness is `r meansprich`.



#### Insert tables by hand


Show as @tbl-byHand for example:


Col A             Col B       Col C                   Col D
------------      -------     ------------------      ------------------
row 1             190         $112 \pm 2$             $233 \pm 3$
$\eta$            0.13        0.12                    0.12
$\eta^2$          0.14        0.13                    0.50
$\eta^3$          0.15        0.31                    0.52

: **Caption** of table by hand. {#tbl-byHand}

More details about tables can be found [here](https://quarto.org/docs/authoring/tables.html).

#### Figures

Insert figure by code chunk. And cross-ref it back as @fig-figName.


```{r}
#| label: fig-figName
#| fig-cap: "**Figure caption here.** With more caption text here."
#| fig-pos: 'H'
#| fig.width: 7
#| fig.asp: 1
#| echo: false
#| message: false
ggplot(data = envi.sprich, aes(x = value, y = sprich)) +
  geom_point() + geom_smooth(method = "lm") +
  facet_wrap(~envi, scales = "free_x") + 
  theme_bw()
```


Or if you already have the figure and want to cite it as @fig-figByHand.


```{r}
#| label: fig-figByHand
#| fig-cap: "**Figure by hand caption here.** With more caption text here."
#| fig-pos: 'H'
#| out.width: '70%'
#| echo: false
knitr::include_graphics(path = here::here("Figs/plot.pdf"))
```



Another example is @fig-figS1 in the Appendix.

More details can be found at [here](https://quarto.org/docs/authoring/figures.html).

# References

::: {#refs}
:::

\clearpage

\setcounter{page}{0}
\pagenumbering{arabic}
\setcounter{page}{1}


\setcounter{figure}{0}
\setcounter{table}{0}
\renewcommand {\thetable}{S\arabic{table}}
\renewcommand {\thefigure}{S\arabic{figure}}


# Supporting Information

Some text here.

## Figures



```{r}
#| label: fig-figS1
#| fig-cap: "**Figure caption here.** With more caption text here."
#| out.width: '70%'
knitr::include_graphics(path = here::here("Figs/plot.pdf"))
```
